\chapter{Semantics}\label{chap:semantics}
%\kri{hvordan indkludere vi semantiken fra sidste raport?}
%\input{documents/semantics/language/language}
%\section{Instruction Semantics}
%\input{documents/semantics/language/rule_examples}
%\input{documents/semantics/language/fault}
In this chapter, the semantics of \jcl and the fault models considered, are briefly described. The full language and fault model semantics can be seen in \cref{chap:semantics}, and are taken in full from from \cite{javasec}. We have made minor contributions to the semantics, thus extending them. As mentioned by \cite{javasec}, \jcl is a variation of the core Java Card bytecode language instructions. By core, it is meant that most of the instructions in the full  Java Card bytecode language can be built from the instructions in \jcl. The language was created to make it easier to model, because of the fewer instructions. There is no prior formalisation of the Java Card bytecode Language known to the authors. The instructions in \jcl and fault models are briefly described in \cref{tab:instr} and \cref{tab:fault}, respectively. 
\input{documents/semantics/language/compressedRules}
\input{documents/semantics/language/compressedFault}

\section{Invoke}
``Virtual methods are instance methods that are resolved dynamically. The set includes all public, protected and package-visible instance methods. Private instance methods and all constructors are not virtual methods, but instead are resolved statically during compilation.'' \cite[chap. 4.3.7.6]{java_card_spec}
